A fast and simple primal-dual algorithm for computing Nash equilibria in two-person zero-sum games

### 2014-12-04 onepage.tex
better algo .tex
more

\begin{document}
%\onecolumn
\title{A fast and simple primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum games}

@@

\section{Introduction}
%\label{sec:intro}

@@

\subsection{Statement of the problem}
We are interested in the problem of computing a Nash equilibrium for a two-person zero-sum sequential game with imcomplete information
and perfect recall (e.g Texas Hold'em Poker, etc.). In the \textit{sequence-form representation} of the game, the problem has the following saddle-point formulation
\begin{equation}
  \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
  \label{eq:opt_pb}
\end{equation}

where $Q_j := \{z \in \mathbb{R}^{n_j}|z \ge 0, E_jz=e_j\}$, for $j \in \{1, 2\}$. As usual, the ``minimize-maximize'' notation in problem
\eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
\begin{equation}
  {y^*}^TAx \le y^TAx \le y^TAx^*, \forall (x, y) \in Q_1 \times Q_2
\end{equation}
Such pairs correspond to the Nash equilibria of the game.

We recall that $E_j$ is a $p_j$-by-$n_j$ matrix whose
entries are $-1$, $0$, or $+1$, and $e_j := (1, 0, 0, ..., 0)$ is a vector of length $p_j$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
encode linear constraints on our (resp. the opponent's)  ``admissible'' realization $x$ (resp. $y$). $A$ is the payoff matrix, of size $n_1 \times n_2$.

\begin{remark}
  In practice, the matrices $A$, $E_1$, and $E_2$ are large but very sparse too.
%% : $A$ will be sparse because a concrete sequential game will
%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
%% combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
%% $E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
%% zig-zag between only a limited number of the player's information sets so that a move at an information set will
%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
This sparsity should be thoroughly exploited by a solver for problem \eqref{eq:opt_pb}.
\end{remark}

@@

We first introduce some fundamental notations, and then proceed to derive the algorithm. The convergence and convergence rate
of our algorithm derive explicitly from the general Chambolle-Pock primal-dual scheme.

\subsection{Notation and Terminology}
Give positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
$\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_j \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegative orthant}.

For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
$(x)_+$ denotes its point-wise maximum with 0. Note that $(x)_+ \in \mathbb{R}^n_+$.
For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$, denoted $\|K\|$, is defined by
\footnote{Equivalently, $\|K\|$ is the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$.}
$\|K\| := \underset{x \ne 0}{max}\text{ }\frac{\|Kx\|}{\|x\|}$.

Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
$i_C(x) = 0$ if $x \in C$ and $i_C(x) = +\infty$ otherwise. Note that $i_{C \cap D} = i_C + i_D$. Finally, given a \textit{proper convex lower semi-continous
function} (\textit{p.c.l.s.c} for short) $f : \mathbb{R}^n \rightarrow [0, +\infty]$, and a positive real number $\tau$, the \textit{proximal operator} of $f$ of rank $\tau$,
denoted $\text{prox}_{\tau f}$ is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) solution of the problem
\begin{equation}
  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
\end{equation}

@@

\subsection{Derivation of the algorithm}
Observe that $\forall (x, y) \in \mathbb{R}^{n_1} \times \mathbb{R}^{n_2}$, we have
\begin{equation}
  \left .
  \begin{split}
    -i_{Q_1}(x) &= -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)}\\
  i_{Q_2}(y) &= i_{\mathbb{R}^{n_2}_+}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}
  \end{split}
  \right\}
\end{equation}
and so problem \eqref{eq:opt_pb} can be re-written in the unconstrained form

@@

where $v \in \mathbb{R}^{p_1}$ and $u \in \mathbb{R}^{p_2}$ are auxiliary dual variables and 
\begin{equation}
  \left .
  \begin{split}
    K :=
    \left[
      \begin{array}{c|c}
        A & -E_1^T \\ \hline
        E_2 & 0_{p_2, p_1}
      \end{array}
      \right] \in \mathbb{R}^{(n_1 + p_2) \times (n_2 + p_1)} \\
    %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)}\\
      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tv\\
      F: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tu
  \end{split}
  \right\}
\end{equation}

It is clear that $G$ and $F$ are \textit{p.c.l.s.c} and a straightforward computation reveals that their proximal operators are given by
\begin{equation}
  \left .
  \begin{split}
    \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{p_1}\\
    (y, v) &\mapsto ((y)_+, v - \tau e_1)\\
  \end{split}
  \right\}
\end{equation}

and
\begin{equation}
  \left .
  \begin{split}
    \text{prox}_{\sigma F}: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{p_2}\\
    (x, u) &\mapsto ((x)_+, u - \sigma e_2)
  \end{split}
  \right\}
\end{equation}

@@

\begin{algorithm}[htb]
  \caption{Primal-dual algorithm for computing a Nash equilibrium of a two-person zero-sum game}
  \textbf{initialize}
  $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{p_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{p_2}$; 
  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$ (for example take $\tau = \sigma = \frac{.99}{\|K\|}$); $k = 0$.\\
  \Repeat{Convergence}{
    \begin{eqnarray*}
      x^{(k+1)} &\leftarrow& \left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)_+\\
      u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
      y^{(k+1)} &\leftarrow& \left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)_+\\
      v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
      \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
      k &\leftarrow& k + 1
    \end{eqnarray*}
  } \Return $x^{(k)}$, $y^{(k)}$
  \label{Tab:algo}
\end{algorithm}

>>>>

\begin{document}
\onecolumn
\title{A fast and simple primal-dual algorithm for computing Nash equilibria in two-person zero-sum games}

@@

\section{Introduction}
\label{sec:intro}

@@

\subsection{Notation and Terminology}
\label{sec:notation}
We will need the following notations and definitions in the sequel. Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
the space of all $m$-by-$n$ real matrices. $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros and $1_{m,n}$ denotes the $m$-by-$n$ matrix of ones.
$\mathbb{R}^n_+$ := $\{x \in \mathbb{R}^n|x_j \ge 0 \text{ }  \forall j\}$ is the $n$-dimensional \textit{nonnegative orthant}.

For a vector $x \in \mathbb{R}^n$, $\|x\|$ denotes the $2$-\textit{norm} of $x$ defined by $\|x\| := \sqrt{x^Tx}$.
$(x)_+$ denotes its point-wise maximum with 0. Note that $(x)_+ \in \mathbb{R}^n_+$.
For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The \textit{spectral norm} of a matrix $K$,
denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).

Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
$i_C(x) = 0$ if $x \in C$ and $i_C(x) = +\infty$ otherwise. Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projector} onto $C$, denoted $\Pi_C$ is the function
$\Pi: \mathbb{R}^n \mapsto C$, which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closed to $x$. Precisely,
\begin{equation}
  \Pi_C(x) := \underset{c \in C}{argimin}\text{ }\|c - x\|^2
\end{equation}
For example, $\Pi_{\mathbb{R}^n_+}(x) = (x)_+, \forall x \in \mathbb{R}^n$.

Let $f : \mathbb{R}^n \rightarrow [0, +\infty]$ be a \textit{proper convex lower semi-continous function} (\textit{p.c.l.s.c} for short), and a positive real number $\tau$, the \textit{proximal operator} of $f$ of rank $\tau$,
denoted $\text{prox}_{\tau f}$ is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) solution of the problem
\begin{equation}
  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
\end{equation}

It is easy to see that if $f$ is the indicator function of a convex set $C$, then $\text{prox}_{\tau f} = \Pi_C, \forall \tau > 0$. In this sense, proximal operators can be seen
as a generalization of euclidean projection operators.
\subsection{Statement of the problem}
We are interested in \textit{two-person zero-sum} games for which the \textit{Nash Equilibrium Problem (NEP)} can be formulated as
\begin{equation}
  \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
  \label{eq:opt_pb}
\end{equation}

where \textit{feasibility sets} $Q_j$ have the form
\begin{equation}
  Q_j := \{z \in C_j|E_jz = e_j\},\text{ for some convex subset $C_j$ of a euclidean space $\mathbb{R}^{n_j}$, and some vector $e_j \in \mathbb{R}^{p_j}$}
\end{equation}
$Q_j$ is the \textit{strategy portfolio} for player $j$. $A$ is the \textit{payoff matrix} from player 1's perspective of the game: if player 1 players strategy
$x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money (and can be in fact negative!, in which case this represents a loss for player 1).
We will assume that the convex sets $C_j$ are simple enough so that the eucliean projectors $\Pi_{C_j}$ can be cheaply computed.
Typically, $C_j = \mathbb{R}^{p_j}_+$, and encodes a nonnegativity constraint; in this case, $\Pi_{C_j}(z) \equiv (z)_+$ as seen in subsection \ref{sec:notation}.
As usual, the ``minimize-maximize'' notation in problem \eqref{eq:opt_pb} means that a pair $(\hat{x}, \hat{y}) \in Q_1 \times Q_2$ is a solution iff
\begin{equation}
  x^TA\hat{y} \le x^TAy \le {\hat{x}}^TAy, \forall (x, y) \in Q_1 \times Q_2
\end{equation}
Such pairs $(\hat{x}, \hat{y})$ correspond to the Nash equilibria of the game, and ${\hat{x}}^TA\hat{y}$ is the \textit{value}
\footnote{This value is the same for every equilibrium pair $(\hat{x}, \hat{y})$.} of the game.

\subsection{Examples}
\label{subsec:example_games}
\begin{itemize}
\item[{\textit{(a)}}] \textit{Simultaneous two-person zero-sum games}\\
  Here, the NEP takes the form of problem \eqref{eq:opt_pb} with $p_j = 1$, $C_j = \mathbb{R}^{p_j}_+$, $E_j = 1_{1, n_j}$,
  and $e_j = 1$, so that $Q_j$ is simply the probabability $n_j$-simplex $\Delta_{n_j}$. Each point in $\Delta_{n_j}$ corresponds to a \textit{mixed-strategy} for player $j$,
and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_j}$).
\item[{\textit{(b)}}] \textit{Two-person zero-sum sequential games with imcomplete information and perfect recall}\\
It is now known, thanks to the \textit{sequence-form representaion}, that the NEP for such games takes the form of problem \eqref{eq:opt_pb}

We recall that in the sequence-form representation of such games,  $E_j$ is a matrix whose
entries are $-1$, $0$, or $+1$, and $e_j := (1, 0, 0, ..., 0)$. We also recall that $E_1$ and $e_1$ (resp. $E_2$ and $e_2$)
encode linear constraints player 1's (resp. player 2's)  ``admissible'' \textit{realization plans} $x$ (resp. $y$).

As an illustration, the pair $(\hat{x}, \hat{y})$ given by
$\hat{x} = (1, .478, .522, .174, .826)$ and
$\hat{y} = (1, 1/2, 1/2)$ is a Nash equilibrium for the sequence-form game given by\\
$A = \left(\begin{array}{ccc}
0 & 0 & 0\\
0 & 0 & 0\\
0 & 1 & -1\\
0 & -2 & 4\\
1 & 0 & 0
\end{array}\right)$, $E_1 = \left(\begin{array}{ccccc}
  1 & 0 & 0 & 0 & 0\\
  -1 & 1 & 1 & 0 & 0\\
  -1 & 0 & 0 & 1 & 1
\end{array}\right)$,
$e_1 = (1, 0, 0)$, $E_2 = \left(\begin{array}{ccc}
  1 & 0 & 0\\
  -1 & 1 & 1
\end{array}\right)$, and $e_2 = (1, 0)$.
\end{itemize}

\begin{remark}
  At least for sequential games, the matrices $A$, $E_1$, and $E_2$ are very large (can have upto billions of rows and columns) but very sparse too.
%% : $A$ will be sparse because a concrete sequential game will
%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
%% combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
%% $E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
%% zig-zag between only a limited number of the player's information sets so that a move at an information set will
%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
This sparsity should be thoroughly exploited by a solver for problem \eqref{eq:opt_pb}.
\end{remark}

@@

We now detail the proposed algorithm for solving the saddle-point problem \eqref{eq:opt_pb}. The convergence and convergence rate
of our algorithm derive explicitly from the general Chambolle-Pock primal-dual scheme.

@@

\subsection{Derivation of the algorithm}
Observe that $\forall (x, y) \in \mathbb{R}^{n_1} \times \mathbb{R}^{n_2}$, we have
\begin{equation}
  \left .
  \begin{split}
    -i_{Q_1}(x) &= -i_{C_1}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)}\\
  i_{Q_2}(y) &= i_{C_2}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}
  \end{split}
  \right\}
\end{equation}
and so problem \eqref{eq:opt_pb} can be re-written in the unconstrained form

@@

where $v \in \mathbb{R}^{p_1}$ and $u \in \mathbb{R}^{p_2}$ are auxiliary dual variables and 
\begin{equation}
  \left .
  \begin{split}
    K :=
    \left[
      \begin{array}{c|c}
        A & -E_1^T \\ \hline
        E_2 & 0_{p_2, p_1}
      \end{array}
      \right] \in \mathbb{R}^{(n_1 + p_2) \times (n_2 + p_1)} \\
    %%\begin{bmatrix}A \text{ } E_1^T\\ E_2 \text{ } 0\end{bmatrix} \in \mathbb{R}^{(n_2 + p_1) \times (n_1 + p_2)}\\
      G: \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} \rightarrow [0, +\infty], (y, v) \mapsto i_{C_2}(y) + e_1^Tv\\
      F: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} \rightarrow [0, +\infty], (x, u) \mapsto i_{C_1}(x) + e_2^Tu
  \end{split}
  \right\}
  \label{eq:unconstrained_pb}
\end{equation}

It is clear that $G$ and $F$ are \textit{p.c.l.s.c} and a straightforward computation reveals that their proximal operators are given by
\begin{equation}
  \left .
  \begin{split}
    \text{prox}_{\tau G} : \mathbb{R}^{n_2} \times \mathbb{R}^{p_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{p_1}\\
    (y, v) &\mapsto (\Pi_{C_2}(y), v - \tau e_1)\\
  \end{split}
  \right\}
\end{equation}

and
\begin{equation}
  \left .
  \begin{split}
    \text{prox}_{\sigma F}: \mathbb{R}^{n_1} \times \mathbb{R}^{p_2} &\rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{p_2}\\
    (x, u) &\mapsto (\Pi_{C_1}(x), u - \sigma e_2)
  \end{split}
  \right\}
\end{equation}

@@

\begin{algorithm}[htb]
  \caption{Primal-dual algorithm so solving the saddle-point problem \eqref{eq:opt_pb}}
  \textbf{require}
  \begin{itemize}
    \item the specification of a game $(A, E_1, E_2, e_1, e_2, C_1, C_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
  $E_1 \in \mathbb{R}^{p_1 \times n_1}$, $E_2 \in \mathbb{R}^{p_2 \times n_2}$, $e_1 \in \mathbb{R}^{p_1}$, $e_2 \in \mathbb{R}^{p_2}$, $C_j$ is a convex subset of $\mathbb{R}^{n_j}$;
      \item a tolerance level $\epsilon > 0$
  \end{itemize}
  \textbf{precompute} $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
  \textbf{initialize}
  $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{p_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{p_2}$; 
  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$ (for example take $\tau = \sigma = \frac{.99}{\|K\|}$); $k = 0$.\\
  \Repeat{$\frac{\|\Delta x^{(k)}\|^2 + \|\Delta v^{(k)}\|^2}{\sigma} + \frac{\|\Delta y^{(k)}\|^2 + \|\Delta u^{(k)}\|^2}{\tau} < \epsilon$}{
    \begin{eqnarray*}
      x^{(k+1)} &\leftarrow& \Pi_{C_1}\left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)\\
      u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
      y^{(k+1)} &\leftarrow& \Pi_{C_2}\left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)\\
      v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
      \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
      k &\leftarrow& k + 1
    \end{eqnarray*}
  } \Return $x^{(k)}$, $y^{(k)}$
  \label{Tab:algo}
\end{algorithm}

\subsubsection{Special case: $C_j = \mathbb{R}^{n_j}_+$} As discussed in subsection \ref{subsec:example_games},
the NEP for two-person zero-sum simultaneous games and two-person zero-sum sequential games with imcomplete
information and perfect admits the formulation \eqref{eq:opt_pb}, with $C_j = \mathbb{R}^{n_j}_+$ (coding for nonnegativity constraints).
In such situations, $\Pi_{C_j}(z) \equiv (z)_+$ as already mentioned in \ref{sec:notation}, and Algorithm \ref{Tab:algo} reduces to the simpler Algorithm \ref{Tab:algo_simplified}.

\begin{algorithm}[htb]
  \caption{Primal-dual algorithm so solving the saddle-point problem \eqref{eq:opt_pb}, with nonnegativity constraints $C_j = \mathbb{R}^{n_j}_+$}
  \textbf{require}
  \begin{itemize}
    \item the specification of a game $(A, E_1, E_2, e_1, e_2)$, where $A \in \mathbb{R}^{n_1 \times n_2}$,
  $E_1 \in \mathbb{R}^{p_1 \times n_1}$, $E_2 \in \mathbb{R}^{p_2 \times n_2}$, $e_1 \in \mathbb{R}^{p_1}$, $e_2 \in \mathbb{R}^{p_2}$;
      \item a tolerance level $\epsilon > 0$
  \end{itemize}
  \textbf{precompute} $\|K\|^2$, where $K$ is constructed as in equations \eqref{eq:unconstrained_pb}. $\|K\|^2$ can be computed via a \textit{power iteration} on $K^TK$, for example.\\
  \textbf{initialize}
  $x^{(0)} \in \mathbb{R}^{n_1}$; $v \in \mathbb{R}^{p_1}$; $\tilde{y^{(0)}}, y^{(0)} \in \mathbb{R}^{n_2}$; $u^{(0)} \in \mathbb{R}^{p_2}$; 
  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$ (for example take $\tau = \sigma = \frac{.99}{\|K\|}$); $k = 0$.\\
  \Repeat{$\frac{\|\Delta x^{(k)}\|^2 + \|\Delta v^{(k)}\|^2}{\sigma} + \frac{\|\Delta y^{(k)}\|^2 + \|\Delta u^{(k)}\|^2}{\tau} < \epsilon$}{
    \begin{eqnarray*}
      x^{(k+1)} &\leftarrow& \left(x^{(k)} + \tau \left(A\tilde{y}^{(k)} - E_1^T\tilde{v}^{(k)}\right)\right)_+\\
      u^{(k+1)} &\leftarrow& u^{(k)} + \tau \left(E_2\tilde{y}^{(k)} - e_2\right)\\
      y^{(k+1)} &\leftarrow& \left(y^{(k)} - \sigma \left(A^Tx^{(k + 1)} + E_2^Tu^{(k + 1)}\right)\right)_+\\
      v^{(k+1)} &\leftarrow& v^{(k)} - \sigma \left(e_1 - E_1x^{(k+1)}\right)\\
      \tilde{y}^{(k+1)} &\leftarrow& 2y^{(k+1)} - y^{(k)}\\
      \tilde{u}^{(k+1)} &\leftarrow& 2u^{(k+1)} - u^{(k)}\\
      k &\leftarrow& k + 1
    \end{eqnarray*}
  } \Return $x^{(k)}$, $y^{(k)}$
  \label{Tab:algo_simplified}
\end{algorithm}

\section{Application to Poker}
\subsection{Kuhn Poker}
The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
$A = \left(\begin{array}{ccccccccccccc}
  &   &   &   &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
\end{array}\right)
 \in \mathbb{R}^{13 \times 13}$,\\
$E_1 = \left(\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
\end{array}\right)  \in \mathbb{R}^{7 \times 13}$, $e_1 = e_2 = (1, 0, 0, 0, 0, 0, 0) \in \mathbb{R}^7$,\\
$E_2 = \left(\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
\end{array}\right)  \in \mathbb{R}^{7 \times 13}$.\\
The pair $(\hat{x}, \hat{y}) \in \mathbb{R}^{13}_+ \times \mathbb{R}^{13}_+$ of realization plans given by $\hat{x} = (1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725)$ and\\
$\hat{y} = (1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1)$ is a Nash equlibrium for the game, computed using Algorithm  \ref{Tab:algo_simplified}. The convergence curve is shown in Fig \ref{Tab:conv_curves}. One easy checks that this equilibrium is feasible. Indeed,  $E_1\hat{x} - e_1 = (4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, -8.62 \times 10^{-7}, -1.96 \times 10^{-5})$ and $E_2\hat{y} - e_2 = (-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6}, 2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7})$. Finally, $\hat{x}^TA\hat{y} = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by Kuhn in his 1954 paper.

\begin{figure}
  \includegraphics[width=.5\linewidth]{Kuhn3112_NE.pdf}
  \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
  \caption{Convergence curves of Algorithm \ref{Tab:algo_simplified} on simplified variants of Poker. \textbf{Left}: Kuhn Poker. \textbf{Right}: Another simplified Poker variant}.
  \label{Tab:conv_curves}
\end{figure}
